\beginsong{4-Chord Song}[by={\normalsize Axis of Awesome}]
\caponote[2]
\beginverse
\[D]My life is brilliant, \[A]my love is pure.
\[H&]I saw an angel, \[G]of this I'm sure.
\[D]Forever you\[A]ng, I wanna
\[H&]be forever youn\[G]g.
\[D]I won't hesita\[A]te no more,
no m\[H&]ore, it cannot \[G]wait, I'm yours.
\[D]This is the way you left me,
\[A]I'm not pretending,
\[H&]No hope, no love, no glory,
\[G]No happy ending.
\[D]Cause you are a\[A]mazing,
\[H&]We did am\[G]azing, \[D]things.
If I could,\[A] then I would,
\[H&]I'll go wher\[G]ever you will, (go)
\[D]Can you \[A]feel, the \[H&]love to\[G]night?
And she \[D]will, be \[A]loved,
Yeah she \[H&]will, be \[G]loved.
Pictures of \[D]you, pictures of \[A]me,
up upon your \[H&]wall for the world to \[G]see.
'cause I cant \[D]live,\[A] with or \[H&]without you.\[G]
And if I \[D]fall, \[A]at your \[H&]feet.\[G]
You'll let your \[D]tears, am I not \[A]pretty enough,\[H&]
is my \[G]heart too broken.

\vspace{0.5cm}
\textit{(Double time!)}

\vspace{0.5cm}

When I \[D]find myself in \[A]times of trouble,
\[H&]Mother mary, \[G]comes to me.\[D]
Sometimes I \[A]feel like I \[H&]dont have a \[G]partner.\[D]
That's the \[A]way it's gonna \[H&]be, little \[G]darlin',\[D]
We'll be \[A]ridin' on the \[H&]horses, \[G]yeah yeah.
\[D]No \[A]woman, no \[H&]cry,
It \[G]surely is a \[D]dream,
I come from the \[A]land down under.\[H&]\[G]
\[D]Once a jolly \[A]swagman, \[H&]camped by a \[G]billabong.
\[D]Take \[A]on \[H&]me,(\[G]When I come around)
\[D]Take \[A]Me \[H&]On,(\[G]When I come around)
\[D]I'll \[A]be \[H&]gone\[G]
In a day or\[D], \[A]two.
\[H&]Save to\[G]night,  (Gonna take a lot to drag me away from you.)
\[D]Fight the break of \[A]dawn.
Come\[H&] tommorow\[G],  (There's nothing that a hundred men or more could ever do.)
to\[D]mmorow I'll be\[A] gone.
\[H&] I k\[G]now she's p\[D]layin with \[A]me,
\[H&] But thats o\[G]kay 'cause I've got \[D]no self-es\[A]teem.
With a \[H&]thousand e\[G]yes and a \[D]good dis\[A]guise,
hit 'em \[H&]right between the e\[G]yes, hit 'em \[D]right between the \[A]eyes.
'Cause \[H&]I'm not h\[G]ere for your e\[D]ntert\[A]ainment,
\[H&]  you don't r\[G]eally wanna m\[D]ess with \[A]me tonight.
\[H&] Cant read my, \[G]cant read my, \[D]no he can't \[A]read my,
\[H&]poker fa\[G]ce, c\[D]ome on Barbie \[A]lets go party.
\endverse


\beginverse
\[H&]Lost and insec\[G]ure, \[D]you found me,\[A] you found me.
\[H&] She wants to touch me (woo-h\[G]oo),
She wants to love me (woo-\[D]hoo),
She'll never leave me (woo-\[A]hoo-oh-oh-oh).
\[H&]   Control yourself,\[G]  take only what you \[D]need from it.\[A]
\[H&]Take your canvas \[G]bags, take your canvas \[D]bags,
Take your canvas \[A]bags, to the supermarket.
\[H&]Take your canvas \[G]bags.
\endverse



\beginverse
Nothings right I'm \[D]torn,
I'm all out of \[A]faith,
this is how I \[H&]feel,
I'm cold and I am \[G]shamed,
lying naked on the \[D]floor.
Illusion never \[A]changed,
into something\[H&] real,
I'm wide awake and \[G]I can see I'm more than a \[D]bird,
I'm more than a p\[A]lane,
I'm a \[H&]bird-plane\[G],
I'm a \[D]bird-plane,\[A]
A mother fucking \[H&]bird-plane.\[G]
\endverse


\beginverse
Doesn't that sound \[D]familiar,
doesn't that sound too \[A]close to home
doesn't that make you \[H&]shiver,
the way things could have \[G]gone.
And doesn't that seem \[D]peculiar,
'cause everyone wants a \[A]little more,
there's something I do re\[H&]member,
to never go this \[G]far,
thats all it takes to be a \[D]star.
\endverse
\endsong
