\beginsong{American Pie}[by={\normalsize Don McLean}]
\transpose{7}
\preferflats
\caponote[5]
\beginverse
A \[G]long, \[D]long \[E&]time ago,
\[A&]I can still re\[C]member,
how that \[E&]music used to make me \[D]smile.
And \[G]I knew if I \[D]had my \[E&]chance,
that \[A&]I could make those \[C]people dance,
and \[E&]maybe they'd by \[C]happy for a \[D]while.
But \[E&]February \[A&]made me shiver,
with \[E&]every paper \[A&]I'd deliver.
\[C]Bad news \[G]on the \[A&]doorstep;
I \[C]couldn't take \[D]one more step
I \[G]can't re\[D]member \[E&]if I cried,
when I \[A&]read about his \[D]widowed bride;
\[G]something \[D]touched me \[E&]deep inside,
the \[C]day the \[D7]music \[G]died\[C].\[G]
\endverse

\beginchorus
So, \[G]bye-\[C]bye, Miss \[G]American \[D]Pie,
drove my \[G]Chevy to the \[C]levee but the \[G]levee was \[D]dry.
Them \[G]good ole \[C]boys were drinking \[G]whiskey and \[D]rye,
singing \[E&]this'll be the day that I \[A7]die,
\[E&]this'll be the day that I \[D7]die.
\endchorus

\beginverse
\[G]Did you write the \[A&]book of love
and do \[C]you have faith in \[A&]God above,
if the \[E&]Bible \[D]tells you so? 
Now do \[G]you be\[D]lieve in \[E&]rock and roll,
can \[A&]music save your \[C]mortal soul?
And \[E&]can you teach me how to \[A7]dance real \[D7]slow?
\endverse
\beginverse
Well I \[E&]know that you're in \[A&]love with him,
'cause I \[E&]saw you dancing \[A&]in the gym
You \[C]both \[G]kicked off your \[A7]shoes,
man I \[C]dig those rhythm and \[D7]blues!
I was a \[G]lonely \[D]teenage \[E&]bronching buck,
with a \[A&]pink carnation and a \[C]pick-up truck.
But I \[G]knew \[D]I was \[E&]out of luck 
the \[C]day, the \[D7]music \[G]die\[C]d.\[G]
\[G]I started \[D7]singing....
\endverse

\refchorus

\beginverse
Now for \[G]ten years, we've been \[A&]on our own
and \[C]moss grows fat on a \[A&]rolling stone,
but \[E&]that's not how it \[D]used to be.
When the \[G]jester \[D]sang for the \[E&]King and
Queen, in a \[A&]coat he borrowed \[C]from James Dean,
and a \[E&]voice that \[A7]came from you and \[D7]me.
\endverse

\beginverse
Oh, and \[E&]while the king was \[A&]looking down,
the \[E&]jester stole his \[A&]thorny crown;
the \[C]court room \[G]was ad\[A7]journed,
no \[C]verdict was re\[D7]turned.
And while \[G]Lenin \[D]read a \[E&]book on Marx,
the \[A&]quartet practiced \[C]in the park;
\[G]and we sang \[D]dirges \[E&]in the dark,
the \[C]day the \[D7]music \[G]die\[C]d,\[G]
we were \[D7]singing
\endverse

\refchorus

\beginverse
\[G]Helter skelter \[A&]in the summer swelter,
the \[C]birds flew off with a \[A&]fallout shelter;
\[E&]eight miles high and falling \[D]fast.
It \[G]landed \[D]foul \[E&]on the grass,
the \[A&]players tried for a \[C]forward pass
with the \[E&]jester on the \[A7]sidelines in a \[D7]cast.
\endverse
\beginverse
The \[E&]half time air was \[A&]sweet perfume,
while the \[E&]sergeants played a \[A&]marching tune;
we \[C]all got \[G]up to \[A7]dance, but we \[C]never got the \[D7]chance.
'Cause the \[G]players \[D]tried to \[E&]take the field, 
but the \[A&]marching band re\[C]fused to yield
Do \[G]you re\[D]call what \[E&]was revealed,
the \[C]day the \[D7]music \[G]die\[C]d?\[G]
We started \[D7]singing
\endverse

\refchorus

\beginverse
Oh, and \[G]there we were all \[A&]in one place
a \[C]generation \[A&]lost in space
with \[E&]no time left, to start a\[D]gain. 
So come \[G]on, Jack be \[D]nimble, \[E&]jack be quick,
\[A&]Jack flash sat on a \[C]candlestick, 
'cause \[E&]fire is the \[A7]devil's only \[D7]friend.
\endverse
\beginverse
And \[E&]as I watched him \[A&]on the stage,
my \[E&]hands were clenched in \[A&]fists of rage.
No \[C]angel \[G]born in \[A7]hell,
could \[C]break that Satan’s \[D7]spell
And as the \[G]flames climbed \[D]high in\[E&]to the night,
to \[A&]light the sacri\[C]ficial rite
I saw \[G]Satan \[D]laughing \[E&]with delight, 
the \[C]day the \[D7]music \[G]died\[C].\[G]
We were \[D7]singing
\endverse

\refchorus

\beginverse
I \[G]met a \[D]girl who \[E&]sang the blues
and I \[A&]asked her for some \[C]happy news
but \[E&]she just smiled and \[D]turned away.
\[G]I went \[D]down to the \[E&]sacred store,
where I \[A&]heard the music \[C]years before,
but the \[E&]man there said the \[C]music wouldn't \[D]play. 
\endverse

\beginverse
And \[E&]in the streets the \[A&]children screamed,
the l\[E&]overs cried and the \[A&]poets dreamed.
But \[C]not a \[G]word was \[A&]spoken,
the \[C]church bells all were \[D]broken.
And the \[G]three men \[D]I ad\[E&]mire most:
the \[A&]Father, Son and the \[D]Holy Ghost
\[G]They caught the \[D]last train \[E&]for the coast
the \[C]day, the \[D7]music \[G]died.
And they were \[D7]singing
\endverse

\beginchorus
So, \[G]bye-\[C]bye, Miss \[G]American \[D]Pie,
drove my \[G]Chevy to the \[C]levee but the \[G]levee was \[D]dry.
Them \[G]good ole \[C]boys were drinking \[G]whiskey and \[D]rye,
singing \[E&]this'll be the day that I \[A7]die,
\[E&]this'll be the day that I \[D7]die.
\endchorus

\beginchorus
And they were \[D7]singing
\[G]Bye-\[C]bye, Miss \[G]American \[D]Pie, drove my \[G]Chevy to the \[C]levee but the
\[G]levee was \[D]dry. Them \[G]good ole \[C]boys were drinking \[G]whiskey and \[D]rye, singing
\[C]this'll be the \[D7]day that I \[G]die\[C]\[G]
\endchorus
\endsong