\beginsong{Comfortably Numb}[by={\normalsize Pink Floyd}]
\beginverse
\[Hsus2]       \[H&]Hello?
Is there anybody \[A]in there?
Just nod if you can \[G]hear me\[G/F#]\[E&]
Is there \[H&]anyone at home?
\[Hsus2]Come on now\[H&]
I hear you're \[A]feeling down
\[G]I can ease \[G/F#]your pai\[E&]n
And get you \[H&]on your feet again
\endverse

\beginverse
\[Hsus2] \[H&]Relax
I'll need some infor\[A]mation first
\[G]Just the basic\[G/F#] fact\[E&]s
Can you \[H&]show me where it hurts?
\endverse

\beginchorus
\[D]There is no pain you are re\[A]ceding
\[D]A distant ship smoke on the ho\[A]rizon
\[G]   Y\[C]ou are only coming through in \[G]waves
 Y\[C]our lips move but I can't hear what you'\[G]re saying
When \[D]I was a child I had a \[A]fever
My \[D]hands felt just like two bal\[A]loons
\[G]  No\[C]w I've got that feeling once a\[G]gain, I can't explain,
You would not \[C]understand, this is not how I \[G]am
\endchorus

\beginverse
\[A]I   \[G]     \[Cadd9]       have be\[G]come comfortably \[D]numb.
\[A]I   \[G]    \[Cadd9]  have be\[G]come comfortably \[D]numb.
\endverse

\beginverse
\[H&]O.K.
Just a little \[A]pinprick
There'll be no more \[G]aaaaa\[E&]aaah!
But you may \[H&]feel a little sick
\[Hsus2]Can you stand \[H&]up?
I do believe it's \[A]working, good
That'll keep you \[G]going through the s\[E&]how
Come \[H&]on it's time to go.
\endverse

\beginchorus
\[D]There is no pain, you are re\[A]ceding
\[D]A distant ship smoke on the ho\[A]rizon
\[G]    \[C]You are only coming through in \[G]waves
   Y\[C]our lips move but I can't hear what you\[G]'re saying
When \[D]I was a child, I caught a \[A]fleeting glimpse
\[D]Out of the corner of my \[A]eye
\[G]    \[C]I turned to look but it was \[G]gone
I cannot put my finger \[C]on it now
The child is grown, the \[G]dream is gone
\endchorus

\beginverse
\[Asus4]And  I  \[A]   \[G]     \[Cadd9] have bec\[G]ome comfortably n\[D]umb.
\endverse

\beginverse
\[H&]\[A]\[G]\[E&]\[H&]
\endverse
\endsong