\beginsong{Hey There Delilah}[by={\normalsize Plain White T's}]
\beginverse
\[D]\[F#&]\[D]\[F#&] \chordskip
\endverse

\beginverse
\[D]Hey there Delilah, what's it \[F#&]like in New York City?
I'm a \[D]thousand miles away, 
but girl to\[F#&]night you look so pretty,
Yes you \[H&]do, 
\[G]Time Square can't \[A]shine as bright as \[H&]you,
I swear it's \[A]true.
\endverse

\beginverse
\[D]Hey there Delilah, don't you \[F#&]worry about the distance,
I'm right \[D]there if you get lonely, 
give this \[F#&]song another listen,
Close your \[H&]eyes, 
\[G]listen to my \[A]voice it's my dis\[H&]guise,
I'm by your \[A]side.
\endverse

\beginchorus
\lrep\[D]Oh it's what you do to \[H&]{me}, \rrep\rep{2} \[A]
\lrep\[D]Oh it's what you do to \[H&]{me}, \rrep\rep{2} 
What you do to \[D]me.
\endchorus

\beginverse
\[D]Hey there Delilah, I know \[F#&]times are getting hard,
But just be\[D]lieve me girl some day, 
I'll pay the \[F#&]bills with this guitar,
We'll have it \[H&]good, 
\[G]we'll have the \[A]life we knew we \[H&]would,
My word is \[A]good.
\endverse

\beginverse
\[D]Hey there Delilah, I've got \[F#&]so much left to say,
If every \[D]simple song I wrote to you, 
would \[F#&]take your breath away,
I'd write it \[H&]all, 
\[G]even more in \[A]love with me you'd \[H&]fall,
We'd have it \[A]all.
\endverse

\beginchorus
\lrep\[D]Oh it's what you do to \[H&]{me}, \rrep\rep{2}\[A]
\lrep\[D]Oh it's what you do to \[H&]{me}, \rrep\rep{2}\[A]
\endchorus

\beginverse
A \[G]thousand miles seems pretty far, 
but \[A]they've got planes and trains and cars,
I'd \[D]walk to you if I had no other \[H&]way
Our \[G]friends would all make fun of us, 
and \[A]we'll just laugh along because,
We \[D]know that none of them have felt this \[H&]way,
De\[G]lilah I can promise you, 
that \[A]by the time that we get through,
The \[H&]world will never ever be the same, 
and you're to \[A]blame.
\endverse

\beginverse
\[D]Hey there Delilah you be \[F#&]good, and don't you miss me,
Two more \[D]years and you'll be done with school, 
and \[F#&]I'll be making history,
Like I \[H&]do, 
\[G]You'll know it's \[A]all because of \[H&]you,
\[G]We can do what\[A]ever we want \[H&]to,
\[G]Hey there De\[A]lilah here's to \[H&]you, 
This one's for \[A]you.
\endverse

\beginchorus
\lrep\[D]Oh it's what you do to \[H&]{me}, \rrep\rep{2}\[A]
\lrep\[D]Oh it's what you do to \[H&]{me}, \rrep\rep{2}
What you do to \[D]me.
Ohh\[H&]h\[D]
\endchorus
\endsong