\beginsong{I Will Survive}[by={\normalsize Gloria Gayner}]
\beginverse
At \[A&]first I was afraid, I was \[D&]petrified,
Kept thinking \[G]I could never live without you \[Cmaj7]by my side.
But then I \[Fmaj7]spent so many nights, thinking \[Hm7b5]how you did me wrong,
And I grew \[Esus4]strong; and I learned \[E]how to get along.
\endverse

\beginverse
But now you're \[A&]back, from outer \[D&]space,
I just walked \[G]in, to find you here, with that sad \[Cmaj7]look upon your face.
I should have \[Fmaj7]changed that stupid lock,
I should have \[Hm7b5]made you leave your key,
If I had \[Esus4]known for just one second, you'd be \[E]back to bother me.
\endverse

\beginchorus
Go on now, \[A&]go; walk out the \[D&]door;
Just turn a-\[G]round now, 'cos you're not \[Cmaj7]welcome any more.
\[Fmaj7]Weren't you the one who tried to \[Hm7b5]hurt me with goodbye?
Did you think I'd \[Esus4]crumble; did you think I'd \[E]lay down and die?
Oh no, not \[A&]I; I will sur-\[D&]vive,
Oh, as \[G]long as I know how to love, I \[Cmaj7]know I'll stay alive.
I've got \[Fmaj7]all my life to live, and I've got \[Hm7b5]all my love to give,
And I'll sur-\[Esus4]vive, I will sur-\[E]vive, I will sur-\[A&]vive...
\endchorus

\beginverse
\[A&]\[D&]\[G]\[Cmaj7]\[Fmaj7]\[Hm7b5]\[Esus4]\[E]
\endverse

\beginverse
It took a\[A&]ll the strength I had not to fall a\[D&]part.
Kept trying har\[G]d to mend the pieces of my bro\[Cmaj7]ken heart.
And I spent \[Fmaj7]oh, so many nights, just feeling \[Hm7b5]sorry for myself,
I used to \[Esus4]cry, but now I \[E7]hold my head up high.
And you see \[A&]me; somebody \[D&]new,
I'm not that \[G]chained up little person, still in \[Cmaj7]love with you.
And so you \[Fmaj7]felt like dropping in and just ex\[Hm7b5]pect me to be free,
Well, now I'm \[Esus4]saving all my loving, for some\[E]one who's loving me.
\endverse

\refchorus

\beginverse
\[A&]\[D&]\[G]\[Cmaj7]\[Fmaj7]\[Hm7b5]\[Esus4]\[E]
\endverse
\endsong