\beginsong{Lemon Tree}[by={\normalsize Fool Garden}]
\transpose{7}
\caponote[8]
\beginverse
\[D&]\[A&]\[D&]\[A&]\[G&]\[A&]\[D&]\[A&]\[D&] \vspace*{-0.5cm}
\endverse
\beginverse
I'm \[D&]sitting here in a \[A&]boring room,
It's \[D&]just another rainy Sunday \[A&]afternoon.
I'm \[D&]wasting my time, \[A&]I got nothing to do.
I'm \[D&]hanging around, I'm \[A&]waiting for you,
But \[G&]nothing ever ha\[A&]ppens - and I \[D&]wonder.\[A&]\[D&]
\endverse

\beginverse
I'm \[D&]driving around \[A&]in my car,
I'm \[D&]driving too fast, I'm \[A&]driving too far.
I'd \[D&]like to change my \[A&]point of view
I \[D&]feel so lonely, I'm w\[A&]aiting for you
But \[G&]nothing ever happens \[A&]- and I\[D&] wonder.\[A&]\[D&]
\endverse

\beginchorus
   I \[F]wonder how, I \[C]wonder why
\[D&]Yesterday you told me 'bout the \[A&]blue blue sky
And \[A#]all that I can \[C]see is just a yellow \[F]lemon tree.\[C7]
I'm \[F]turning my head \[C]up and down,
\[D&]I'm turning turning turning turning \[A&]turning around

\prefersharps
And \[A#]all that I can \[Hdim7]see is just another\[C] lemon tree\[C7].
\endchorus

\preferflats
\beginverse
\[D&]Dam....\[A&]\[D&]\[A&]\[G&]\[A&]\[D&]\[A&]\[D&]
\endverse

\beginverse
I'm si\[D&]tting here, I m\[A&]iss the power.
I'd l\[D&]ike to go out, t\[A&]ake in a shower,
But \[D&]there's a heavy cloud \[A&]inside my head.
I fe\[D&]el so tired, put my\[A&]self into bed,
Where \[G&]nothing ever \[A&]happens - and \[D&]I wonder.\[A&]\[D&]
\endverse

\beginverse
\[A]Isolation - \[D&]Is not good for me,
\[C]Isolation - \[F]I don't want to \[A]sit on a lemon tree.
\endverse

\beginverse
I'm \[D&]stepping around in a \[A&]desert of joy
\[D&]Baby anyhow I'll get an\[A&]other toy
And \[G&]everything will\[A&] happen - and \[D&]you wonder. \[A&]\[D&]
\endverse

\refchorus

\beginverse
I \[F]wonder how, I \[C]wonder why
\[D&]Yesterday you told me 'bout the \[A&]blue blue sky
And \[A#]all that I can \[C]see, and \[A#]all that I can \[C]see,
And \[A#]all that I can \[C]see is just a yellow \[F]lemon tree.
\endverse
\endsong