\beginsong{Livin' On A Prayer}[by={\normalsize Bon Jovi}]
\beginverse
\[C] (Once upon a time,\[D]  not so long a\[E&]go)
\endverse

\beginverse
\[E&]Tommy used to work on the docks\[Emadd9]
\[E&]Union's been on strike. He's down on his luck
It's t\[C]ough,  \[D]  so tough.\[E&]
\endverse

\beginverse
\[E&]Gina works the diner all day\[Emadd9]
\[E&]Working for her man. She brings home her pay
For lo\[C]ve,   \[D]  for love.\[E&]
\endverse

\beginverse
She says we've got to \[C]hold \[D]on to what we've \[E&]got.
It \[C]doesn't make a \[D]difference if we make it or \[E&]not.
We've \[C]got each \[D]other and that's a \[E&]lot, for \[C]love.
We'll \[D]give it a shot.
\endverse

\beginchorus
\[E&]Oh, \[C]  we're \[D]halfway there, \[G]woah \[C]oh, \[D7sus4]livin' on a prayer.
\[E&]Take my \[C]hand, we'll \[D]make it I swear
\[G]Woah \[C]oh, \[D7sus4]livin' on a prayer. \[E&]
\endchorus

\beginverse
\[E&]Tommy's got his six string in hock.\[Emadd9]
\[E&]Now he's holding in, what he used to make it talk
So t\[C]ough,\[D] it's  t\[E&]ough.
\endverse

\beginverse
\[E&]Gina dreams of running away\[Emadd9]
\[E&]When she cries in the night, Tommy whispers:
Baby it's O\[C].K.,\[D]  som\[E&]e day.
\endverse

\beginverse
We've got to \[C]hold \[D]on to what we've \[E&]got.
It \[C]doesn't make a \[D]difference if we make it or \[E&]not.
We've \[C]got each \[D]other and that's a \[E&]lot, for \[C]love.
We'll \[D]give it a shot.
\endverse

\beginchorus
\[E&]Oh, \[C]  we're \[D]halfway there, \[G]woah \[C]oh, \[D7sus4]livin' on a prayer.
\[E&]Take my \[C]hand, we'll \[D]make it I swear
\[G]Woah \[C]oh, \[D7sus4]livin' on a prayer.
\[Csus2]Livin' on a prayer.
\endchorus

\beginverse
\[E&]\[C]\[D]\[G]\[C]\[D] \vspace{-0.5cm}
\endverse
\beginverse
\[E&]Ooh, we've got to \[C]hold \[D]on, ready or \[E&]not.
You \[C]live for the fight when that's \[D]all that you've got.
\endverse

\beginverse
\[G&]Woooo\[D#]oo, we're \[F]halfway there
\[B]Woah \[D#]oh, \[F]livin' on a prayer.
\[G&]Take my \[D#]hand and we'll \[F]make it I swear
\[B]Woah \[D#]oh, \[F]livin' on a prayer.
\endverse
\endsong