\beginsong{Nightswimming}[by={\normalsize R.E.M.}]
\beginverse
\[G]\[Cadd9]\[G]\[D] \vspace*{-0.5cm}
\endverse

\beginverse
\[G]           Night swim\[Cadd9]ming\[D]
\[G]deserves  a quiet \[Cadd9]night.\[A7sus4]
\[Cadd9]                  \[D]      \[D]
The \[G] photograph on the \[Cadd9]dashboar\[D]d,
\[G] taken    years   \[Cadd9]ago,\[A7sus4]
\[Cadd9]turned around backwards so the \[D]windshield \[D]shows.
\[G]Every streetlight\[Cadd9]        r\[D]eveals the
\[G]picture   in   re\[Cadd9]verse.\[A7sus4]
\[Cadd9]Still it's so much \[D]clearer.\[D]
\[G]I  forgot  my    \[Cadd9]shirt  a\[D]t the
\[G]water's edge. The \[Cadd9]moon is \[A7sus4]low
to\[Cadd9]night.\[D] \[D]
\endverse

\beginverse
\[G]\[Cadd9]\[G]\[D] \vspace*{-0.5cm}
\endverse

\beginverse
\[G]           Night swim\[Cadd9]ming\[D]
\[G]deserves  a quiet \[Cadd9]night.  \[A7sus4]
I'm \[Cadd9]not sure all these \[D]people
\[D]under\[G]stand.       It's \[Cadd9]not like \[D]years
\[G]ago.           The \[Cadd9]fear  of \[A7sus4]getting
\[Cadd9]caught,        of \[D]reckless\[D]ness and
\[G]water.       They \[Cadd9]cannot  \[D]see me
\[G]naked.      These \[Cadd9]things  they \[A7sus4]go
a\[Cadd9]way,            re\[D]placed  by  \[D]every\[G]day
\endverse

\beginverse
\[G]     Night swim\[Cadd9]ming\[D]
\[G]remembering  that \[Cadd9]night.  \[A7sus4]
Sep\[Cadd9]tember's  coming \[D]soon.     \[D]I'm
\[G]pining  for  the \[Cadd9]moon.   \[D]And
\[G]what if there were \[Cadd9]two  \[A7sus4]side by
\[Cadd9]side in orbit    \[D]around the \[D]fairest
\[G]sun?         That \[Cadd9]bright, \[D]tight
for\[G]ever drum can\[Cadd9]not de\[A7sus4]scribe
night\[Cadd9]swimming.\[D]\[D]
\endverse

\beginverse
\[G]You, I thought I \[Cadd9]knew you\[D].
\[G]You,  I  cannot \[Cadd9]judge.\[A7sus4]
\[Cadd9]You, I thought you \[D]knew me. \[D]This one's
\[G]laughing    quiet\[Cadd9]ly      \[D]under-
\[G]neath  my breath.\[Cadd9]         \[A7sus4]
Night\[Cadd9]swimming.\[D]\[D]
\endverse

\beginverse
\[G]\[Cadd9]\[G]\[D] \vspace*{-0.5cm}
\endverse

\beginverse
\[G]The photograph re\[Cadd9]flects  \[D]every
\[G]streetlight \[Cadd9]{a remin}\[A7sus4]der. Night-
\[Cadd9]swimming   de\[D]serves a quiet
\[G]night.\[Cadd9]\[D]
\[G]            de\[Cadd9]serves \[A7sus4]a quiet
\[Cadd9]night.\[D]\[D]
\endverse

\beginverse
\[G]\[Cadd9]\[G]\[D] \vspace*{-0.5cm}
\endverse
\endsong