\beginsong{The Scotsman}[by={\normalsize The Irish Rovers}]
\beginverse
Well \[D]Scotsman clad in \[G]kilt left the \[A]bar one evening \[D]fair
\[D]One could tell by \[G]how he walked, that he'd \[D]drunk more than his \[A]share.
He \[G]stumbled on un\[D]til he could no \[G]longer keep his \[A]feet,
Then he \[D]staggered off i\[G]nto the grass to \[A]sleep beside the \[D]street.
\endverse

\beginchorus
\[G]Ring ding diddle iddle I dee oh, \[D]ring di diddle I \[A]Oh
He \[D]staggered off i\[G]nto the grass to \[A]sleep beside the \[D]street.
\endchorus

\beginverse
Later\[D] on two \[G]young and lovely \[A]girls just happened \[D]by,
\[D]One says to the \[G]other with a \[D]twinkle in her \[A]eye.
\[G]See yon sleeping \[D]Scotsman, so \[G]strong and handsome \[A]built,
I won\[D]der if it's \[G]true what they don't \[A]wear beneath the\[D] kilt.
\endverse

\refchorus (I wonder...)

\beginverse
They \[D]crept up to that \[G]sleeping Scotsman \[A]quiet as could \[D]be,
\[D]Lifted up his \[G]kilt above the \[D]waist so they could \[A]see.
\[G]And there behold for \[D]them to view ben\[G]eath his Scottish \[A]skirt,
Was n\[D]othing more than \[G]God had graced him \[A]with upon his \[D]birth.
\endverse

\refchorus (Was nothing...)

\beginverse
They \[D]marveled for a \[G]moment then one \[A]said we'd best be \[D]gone,
\[D]Let's leave a present \[G]for our friend \[D]before we move \[A]along.
\[G]As a gift they left a \[D]blue silk ribbon, \[G]tied into a \[A]bow,
Aroun\[D]d the bonnie \[G]star of the Scots \[A]kilt lifting \[D]show.
\endverse

\refchorus (Around the bonnie...)

\beginverse
The S\[D]cotsman woke to n\[G]ature's call and \[A]stumbled towards a \[D]tree,
\[D]Behind a bush he \[G]lifts his kilt and \[D]gawks at what he \[A]sees.
\[G]Then in a startled \[D]voice he says to \[G]what's before his \[A]eyes,
Oh \[D]lad I dunno \[G]where you've been but I \[A]see you've won first \[D]prize.
\endverse

\refchorus (My friend...)
\endsong
