\beginsong{Snow (Hey Oh)}[by={\normalsize Red Hot Chilli Peppers}]
\caponote[4]
\beginverse
\[E&]\[C]\[G]\[D] \rep{4} \vspace{-0.5cm}
\endverse

\beginverse
    \[E&]Come to decide that the \[C]things that I tried
    Were \[G]in my life just \[D]to get high on.
\[E&]    When I sit alone, \[C]come, get a little known,
    \[G]But I need more than my\[D]self this time.
    \[E&]Step from the road to the \[C]sea to the sky,
    And I \[G]do believe that \[D]we rely on.
\[E&]    When I lay it on,\[C] come, get to play it on, \[G]all my life to sa\[D]crifice.
\endverse

\beginverse
    \[E&]Hey o\[C]h,     \[G]  listen \[D]what I \[E&]say, \[C]oh.\[G]\[D]
    I got your, \[E&]hey o\[C]h,    \[G]    now listen \[D]what I \[E&]say, \[C]oh.\[G]\[D]
\endverse

\beginverse
    \[E&]When will I know that I \[C]really can't go
    To the \[G]well once more, time \[D]to decide on.
\[E&]    When it's killing me, \[C]when will really see,
    \[G]All that I need to \[D]look inside?
    \[E&]Come to believe that I \[C]better not leave,
    Be\[G]fore I get my \[D]chance to ride.
\[E&]    When it's killing me, \[C]what do I really need,
    \[G]All that I need to \[D]look inside?
\endverse

\beginverse
    \[E&]Hey o\[C]h,   \[G]    listen \[D]what I \[E&]say, \[C]oh.\[G]\[D]
    Come back and, \[E&]hey \[C]oh,   \[G]      look at \[D]what I \[E&]say, \[C]oh.\[G]\[D]
\endverse

\beginchorus
The \[C]more I see, the less I know,
The more I like to let it go, \[E&]hey oh, oh oh \[C]oh.
\[G]Deep beneath the cover of an\[D]other perfect wonder,
Where it's \[A&]so white as snow.
\[G]Privately divided by a \[D]world so undecided,
And there's \[A&]nowhere to go.
\[G]In between the cover of a\[D]nother perfect wonder,
Where it's \[A&]so white as snow.
\[G]Running through the field where all my \[D]tracks will be concealed,
And there's \[A&]nowhere to go.
\endchorus

\beginverse
\[E&]\[C]\[G]\[D] \rep{2} \vspace{-0.5cm}
\endverse

\beginverse
    \[E&]When to descend to a\[C]mend for a friend,
    All the \[G]channels that have \[D]broken down.
\[E&]    Now you bring it up, \[C]I'm gonna ring it up,
    \[G]Just to hear you \[D]sing it out.
    \[E&]Step from the road to the \[C]sea to the sky,
    And I \[G]do believe what \[D]we rely on.
\[E&]    When I lay it on, \[C]come, get to play it on, \[G]all my life to \[D]sacrifice.
\endverse

\beginverse
    \[E&]Hey o\[C]h,   \[G]    listen \[D]what I \[E&]say, \[C]oh.\[G]\[D]
    I got your, \[E&]hey \[C]oh,   \[G]     listen \[D]what I \[E&]say, \[C]oh.\[G]\[D]
\endverse


\refchorus

\beginverse
    I said, \[G]hey, hey \[D]yeah, oh \[A&]yeah, tell my love now!
    \[G]Hey, hey \[D]yeah, oh \[A&]yeah, tell my love now!
\endverse


\beginverse
\[G]\[D]\[A&]
\endverse
\endsong