\beginsong{Sound of Silence}[by={\normalsize Simon \& Garfunkel}]
\beginverse
\[A&]   Hello darkness, my old \[G]friend,
I've come to talk with you \[A&]again,
Because a vision soft\[F]ly creep\[C]ing,
Left its seeds while I \[F]was slee\[C]ping,
And the \[F]vision that was planted in my \[C]brain
Still remains\[A&]
\[C]Within the s\[G]ound of s\[A&]ilence.
\endverse

\beginverse
In restless dreams I wal\[G]ked alone
Narrow streets of cobble\[A&]stone,
'neath the halo of \[F]a street \[C]lamp,
I turned my collar to the \[F]cold and \[C]damp
When my \[F]eyes were stabbed by the flash of a neon \[C]light
That split the night\[A&]
A\[C]nd touched the \[G]sound of \[A&]silence.
\endverse

\beginverse
And in the naked light I \[G]saw
Ten thousand people, maybe \[A&]more.
People talking with\[F]out spea\[C]king,
People hearing with\[F]out liste\[C]ning,
People writing \[F]songs that voices never \[C]share
And no one dare\[A&]
\[C]Disturb the \[G]sound of \[A&]silence.
\endverse

\beginverse
Fools said I, you do not \[G]know
Silence like a cancer \[A&]grows.
Hear my words that I \[F]might teach \[C]you,
Take my arms that I \[F]might reach \[C]you.
But my \[F]words like silent raindrops \[C]fell,\[A&]
And\[C] echoed
In the \[G]wells of \[A&]silence
\endverse

\beginverse
And the people bowed and \[G]prayed
To the neon God they \[A&]made.
And the sign flashed out \[F]its war\[C]ning,
In the words that it w\[F]as for\[C]ming.
And the sign said, the \[F]words of the prophets
Are written on the subway w\[C]alls
And tenement \[C]halls.\[A&]
And whisp\[C]er'd in the \[G]sounds of \[A&]silence.
\endverse
\endsong