\beginsong{Star of the County Down}[by={\normalsize Irish Rovers}]
%https://www.youtube.com/watch?v=dfUxmRNS3kI

\beginverse
In \[E&]Banbridge Town in the \[G]County\[D] Down
One \[E&]morning last \[D]July,
Down a \[E&]boreen \[C]green come a\[G] sweet co\[D]lleen
And she \[E&]smiled as she \[E&]passed \[D]me \[E&]by.
\endverse
\beginverse
She \[G]looked so sweet from her \[D]two bare feet
To the \[E&]sheen of her nut brown \[D]hair.
Such a \[E&]winsome \[C]elf, I'm \[G]ashamed of m\[D]yself
For to \[E&]see I was \[E&]star\[D]ing \[E&]there.
\endverse

\beginchorus
From \[G]Bantry Bay up to \[D]Derry Quay and
From \[E&]Galway to Dublin \[D]Town,
No \[E&]maid I've \[C]seen like the\[G] fair co\[D]lleen
That I \[E&]met in the \[E&]Coun\[D]ty \[E&]Down.
\endchorus

\beginverse
As she \[E&]onward sped, sure I \[G]scratched my \[D]head,
And I \[E&]looked with a feelin' \[D]rare,
And I \[E&]says, says \[C]I, to a\[G] passer\[D]-by,
"Who's the \[E&]maid with the \[E&]nut \[D]brown \[E&]hair?"
\endverse
\beginverse
He \[G]smiled at me and he \[D]says, says he,
"That's the \[E&]gem of Ireland's \[D]crown.
Young \[E&]Rosie Mc\[C]Cann from the\[G] banks of the\[D] Bann,
She's the \[E&]star of the \[E&]Coun\[D]ty \[E&]Down."
\endverse

\refchorus

\beginverse
She'd \[E&]soft brown eyes with a \[G]look so \[D]shy
And a \[E&]smile like the rose in \[D]June
And she \[E&]sang so \[C]sweet, what a\[G] lovely\[D] treat
As she \[E&]lilted an \[E&]Iris\[D]h \[E&]tune.
\endverse
\beginverse
At the \[G]Lambeth dance I was \[D]in a trance
as she \[E&]whirled with the lads of the \[D]town,
And it \[E&]broke my \[C]heart just to\[G] be \[D]apart
from the \[E&]star of the \[E&]Coun\[D]ty \[E&]Down.
\endverse

\refchorus

\beginverse
At the \[E&]Harvest Fair she'll be \[G]surely \[D]there
And I'll \[E&]dress in my Sunday \[D]clothes,
With my \[E&]shoes shone \[C]bright and my\[G] hat cocked\[D] right
For a \[E&]smile from my \[E&]nut \[D]brown \[E&]rose.
\endverse
\beginverse
No \[G]pipe I'll smoke, no \[D]horse I'll yoke
Till my \[E&]plough turns rust coloured \[D]brown.
And a \[E&]smiling \[C]bride by my\[G] own fir\[D]eside
Sits the \[E&]star of the \[E&]Coun\[D]ty \[E&]Down.
\endverse

\refchorus
\endsong