\beginsong{The Fox The Crow And The Cookie}[by={\normalsize mewithoutyou}]
\transpose{-2}
\caponote[2]
\beginverse
\[H&]  Through mostly \[F#&]vacant streets, 
a \[A]baker from the \[E]outskirts of his \[H&]town
Earned his \[F#&]living peddling \[A]sweets 
from the ragged \[E]cart he dragged a\[H&]round.
The clever \[F#&]fox crept close be\[A]hind, 
kept an \[E]ever-watchful \[H&]eye
For a chance to \[F#&]steal a ginger \[A]spice cake 
or a \[E]boysenberry \[H&]pie.
\endverse

\beginverse
\[F#&]\[A]\[E]\[H&] \vspace*{-0.5cm}
\endverse

\beginverse
Looking \[F#&]down was the hungry \[A]crow, 
"When the \[E]time is right, I'll \[H&]strike
And conde\[F#&]scend to the earth be\[A]low 
and take which\[E]ever treat I'd \[H&]like."
The moment the \[F#&]baker turned a\[A]round 
to shoo the \[E]fox off from his \[H&]cart,
The crow swooped \[F#&]down and snatched
a \[A]shortbread cookie and a \[E]German chocolate \[A]tart.
\endverse

\beginchorus
Using most unfriendly \[E]words 
that the village children had not yet \[D]heard,
the baker shouted threats by \[E]canzonette 
to curse the crafty \[A]bird.
"You rotten wooden mixing \[E]spoon! 
Why you midnight winged ra\[D]coon!
You better bring those pastries \[E]back, 
you no-good burned-black maca\[H&]roon!"
\endchorus

\beginverse
\[F#&]\[A]\[E]\[H&]
\endverse

\beginverse
The fox ap\[F#&]proached the tree where the \[A]bird was perched, 
de\[E]lighted in his \[H&]nest.
"Brother \[F#&]Crow, don't you remember \[A]me? 
It's your old friend \[E]Fox with a humble re\[H&]quest.
If you could \[F#&]share just a modest \[A]piece, 
seeing as I dis\[E]tracted that awful \[H&]man."
This failed to per\[F#&]suade the crow in the \[A]least, 
so the fox re\[E]thought his plan.\[H&]
\endverse

\beginverse
"Then if your lovely \[F#&]song would grace my \[A]ears, 
or to \[E]even hear you \[H&]speak,
Would ease my \[F#&]pains and fears." 
The \[A]crow looked down with a \[E]candy in his \[H&]beak.
"Your poems of \[F#&]wisdom, my good \[A]crow, 
what a \[E]paradise they \[H&]bring!"
This flattery \[F#&]pleased the proud bird, \[A]so 
he opened his \[E]mouth and began to \[A]sing:
\endverse

\beginchorus
"Your subtle acclamation's \[E]true! 
Best to give praise where praise is \[D]due.
Every rook and jay in the \[E]Corvidae's 
been raving about me \[A]too.
They admire me, one and \[E]all. 
Must be the passion in my \[D]caw!
My slender bill known through the \[E]escadrille, 
my fierce commanding \[H&]claw!"
\endchorus

\beginverse
\[A]\[D]\[E]\[A] \hspace{-0.5cm}
\endverse

\beginchorus
I got a walnut brownie \[E]brain, 
and molasses in my \[D]veins,
Crushed graham cracker crust, 
my \[E]powdered sugared funnel cake co\[A]caine.
\endchorus
\beginchorus
Let the crescent cookie \[E]rise. 
These carob colored almond \[D]eyes
Would rest to see my cashewed \[E]princess 
in the swirling marble \[A]sky.
Will rest upon the \[E]knee,
where all the visions cease to \[D]be
A root beer float in our ba\[E]nana boat 
across the tapioca \[A]sea.
When letting all attachments \[E]go, 
is the only prayer we \[D]know,
May it be so, may it be \[E]so, may it be so, \[A]oh.
\endchorus
\endsong