\beginsong{The Unforgiven}[by={\normalsize Metallica}]
\beginverse
\[A&]New blood joins this e\[E&]arth  and q\[D]uickly he's sub-\[A&]dued.
Through constant pain dis\[E&]grace, the \[D]young boy learns their \[A&]rules.
With time the child draws \[E&]in this w\[D]hipping boy done w\[A&]rong.
Deprived of all his t\[E&]houghts, the \[D]young man struggles \[A&]on and  on.
He knows,  a  v\[C]ow unto  his o\[G]wn that n\[A&]ever from this day
his w\[C]ill they'll take a - \[G]way.\[E]\[A&]
\endverse

\beginchorus
\[A&]What I've f\[C]elt, what I've k\[G]nown never s\[E&]hined through in what I've s\[A&]hown.
N\[A&]ever \[C]be, never s\[G]ee. Won't s\[E]ee what might have b\[A&]een.
W\[A&]hat I've f\[C]elt, what I've k\[G]nown, never s\[E&]hined through in what I've s\[A&]hown.
N\[A&]ever f\[C]ree, never \[G]me. So I \[E]dub the unfor\[A&]given.
\endchorus

\beginverse
T\[A&]hey dedicate their l\[E&]ives to r\[D]unning all of \[A&]his
He tries to please them \[E&]all, this b\[D]itter man he \[A&]is
Throughout the life the s\[E&]ame, he's b\[D]attled constan\[A&]tly
This fight he cannot w\[E&]in. A t\[D]ired man they s\[A&]ee no longer cares.
The o\[C]ld man then p\[G]repares to d\[A&]ie regretfully
That o\[C]ld man here is \[G]me.\[E]\[A&]
\endverse

\refchorus \rep{2}

\beginverse
\lrep Never f\[C]ree, never \[G]me. So I \[E]dub the unfor\[A&]give\[C]\[G]n.\[E&]
\[A&]You label \[C]me, I label \[G]you. So I \[E]dub the unfor\[A&]give\[C]\[G]n. \[E&]\[A&] \rrep \rep{2}
Never f\[C]ree, never \[G]me. So I \[E]dub the unfor\[A&]give\[C]\[G]n.\[E&]
\endverse
\endsong