\beginsong{Welcome To The Internet}[by={\normalsize Bo Burnham}]
\beginverse
\[D&]Welcome to the internet, have a look around.
\[G&]Anything that brain of yours can think of can be found.
We've got \[F]mountains of content 
-- some better, some worse.
If \[A7]none of it's of interest to you, you'd be the first.
\endverse

\beginverse
\[D&]Welcome to the internet, come and take a seat.
Would you \[G&]like to see the news or any famous women's feet?
There's \[F]no need to panic, this isn't a test (huh huh).
J\[A7]ust nod or shake your head and we'll do the rest.
\endverse

\beginverse
\[D&]Welcome to the internet, what would you prefer?
Would you \[G&]like to fight for civil rights  or tweet a racial slur?
Be \[F]happy. Be horny. Be bursting with rage.
\[A7]We got a million different ways to engage.
\endverse

\beginverse
\[D&]Welcome to the internet, put your cares aside.
Here's a \[G&]tip for straining pasta.
Here's a nine-year-old who died.
We got \[F]movies, and doctors, and fantasy sports.
And a \[A7]bunch of colored pencil drawings of all the characters of Harry Potter fucking
\[D&]each other.
\endverse

\beginverse
Welcome to the internet, hold on to your socks.
'cause a \[G&]random guy just kindly sent you photos of his cock.
They are \[F]grainy and off-putting. He just sent you more.
\[A7]Dont act surprised, you know you like it, you whore.
\endverse

\beginverse
\[D&]See a man beheaded. 
Get offended, see a shrink.
Show us \[G&]pictures of your children.
 Tell us every thought you think.
Start a \[F]rumor, buy a broom 
or send a death threat to a boomer.
Or \[A7]DM a girl and groom her. 
Do a Zoom or find a tumor in your-
\endverse

\beginverse
\[D&]Here's a healthy breakfast option.
 You should kill your mom.
Here's why \[G&]women never fuck you. 
Here's how you can build a bomb.
Which \[F]Power Ranger are you? 
Take this quirky quiz.
O\[A7]bama sent the immigrants 
to \[A7]vac\[G&]cin\[F]ate \[E]your \[D&]kids.
\endverse

\beginchorus
Could I i\[D&]nterest you in everything, all of the time?
A \[G&]little bit of everything. All of the time.
\[F]Apathy's a tragedy and boredom is a crime.
\[A7]Anything and everything. All of the time.
\endchorus

\rep{2}

\beginverse
\[D&]\[C]\[B]\[A7] \vspace*{-0.5cm}
\endverse

\beginverse
\[D&]You know, \[C]it wasn't always like \[B]this\[A7]
\[D&]Not very \[C]long ago
\[B]Just before your \[A7]time
\[D&]Right before \[C]the towers fell
\[B]Circa '99\[A7]
\endverse

\beginverse
This was \[G&]catalogues
T\[D&]ravel blogs
\[A7]A chat room or \[D&]two
We \[G&]set our sights and \[D&]spent our nights
\[A7]Waiting\[C7]
\endverse

\beginverse
For \[Fmaj7]you
\[Dm7]You
In\[Gm7]satiable \[C7]you
Mommy \[Fmaj7]let you use her i\[Dm7]Pad
\[Gm7]You were barely \[C7]two
And it \[Dm]did all the \[Dmmaj7/C#]things
We \[Dm7/C]designed it to \[B]do
\endverse

\beginverse
Now \[B]look at you
Oh, \[C]look at you
\[D]You
\endverse

\beginverse
\[Gmaj7]You\[Em7]
Un\[Am7]stoppable, w\[D7]atchable
Your \[Gmaj7]time is now. Your i\[Em7]nside's out.
\[Am7]Honey, how you \[D7]grew
And if \[Em]we stick \[Emmaj7/D#]together
Who \[Em7/D]knows what we'll \[A]do
It was \[C]always the pl\[D]an
To put the \[H7]world in your h\[C]and
\endverse

\beginverse
\[E&](cha cha cha...)
\endverse

\beginchorus
Could I i\[E&]nterest you in everything, all of the time?
A \[A&]bit of everything. All of the time.
\[G]Apathy's a tragedy and boredom is a crime.
\[H7]Anything and everything. All of the time.
\endchorus

\beginchorus
Could I i\[E&]nterest you in everything, all of the time?
A \[A&]little bit of everything. All of the time.
\[G]Apathy's a tragedy and boredom is a crime.
\[H7]Anything and everything
\[H7]And anything and everything
\[H7]And anything and everything
All of the time
\endchorus
\endsong