\beginsong{Welcome to My Life}[by={\normalsize Simple Plan}]
\caponote[1]
\beginverse
Do you \[C]ever feel like breaking down?
Do you \[A&]ever feel out of place?
Like \[F]somehow you just don't belong,
and \[G]no one understands you.
Do you \[C]ever wanna run away?
Do you \[A&]lock yourself in your room?
With the \[F]radio on turned up so loud
That \[G]no one hears you screaming.
\endverse

\beginverse
No you \[F]don't know what its like
When \[A&]nothing feels alright
You \[F]don't know what its like to be like \[G]me
\endverse

\beginchorus
To be \[A&]hurt, to feel \[F]lost, to be \[C]left out in the \[G]dark
To be \[A&]kicked when you're \[F]down, to feel like \[C]you've been pushed a\[G]round
To be \[A&]on the edge of \[F]breaking down, when \[C]no one's there to \[G]save you
No you \[D&]don't know what its like \[F]
Welcome to my \[C]life
\endchorus

\beginverse
Do you \[C]wanna be somebody else?
Are you \[A&]sick of being so left out?
Are you \[F]desperate to find something more,
\[G]before your life is over?
Are you \[C]stuck inside a world you hate?
Are you \[A&]sick of everyone around?
With the \[F]big fake smiles and stupid lies,
While \[G]deep inside you're bleeding
\endverse

\beginverse
\[F]No you don't know what its like
When \[A&]nothing feels alright
You \[F]don't know what its like to be like \[G]me
\endverse

\refchorus

\beginverse
\[F]No one ever lies straight to your face
And \[A&]no one ever stabs you in the back
\[F]You might think I'm happy
But I'm \[C]not gonna be \[G]okay
\[F]Everybody always gave you what you wanted
You \[A&]never had to work it was always there
You \[F]don't know what it's like what it's \[G]like..
\endverse

\beginchorus
To be \[A&]hurt, to feel \[F]lost, to be \[C]left out in the \[G]dark
To be \[A&]kicked when you're \[F]down, to feel like \[C]you've been pushed a\[G]round
To be \[A&]on the edge of \[F]breaking down, when \[C]no ones there to \[G]save you
\[D&]No you don't know what its like, what its \[F]like
To be \[A&]hurt, to feel \[F]lost, to be \[C]left out in the \[G]dark
To be \[A&]kicked when you're \[F]down, to feel like \[C]you've been pushed a\[G]round
To be \[A&]on the edge of \[F]breaking down, when \[C]no ones there to \[G]save you
No you \[D&]don't know what its like \[F]
  Welcome to my \[C]life\[A&]
Welcome to my \[F]life\[G]
Welcome to my \[C]life
\endchorus
\endsong